Placing the spotted T Tauri star LkCa 4 on an HR diagram

### 2016-08-02 document/ms.tex
Add software references, but the software command requires AASTEX6

\providecommand{\eprint}[1]{\href{http://arxiv.org/abs/#1}{#1}}
\providecommand{\adsurl}[1]{\href{#1}{ADS}}
\newcommand{\name}{LkCa4 }
%\def\vsini{$v\sin{i_*}$}

@@

Spectroscopic strategies have the power to measure both the starspot areal coverage and temperature in any geometric configuration.  At low resolution, SED modeling \citep{wolk96} has detected evidence for sunspots in weak-lined T-Tauri stars (WTTS).  At high resolution, line depth ratio analysis has historically been demonstrated on evolved stars in relatively small bandwidths, namely the TiO bands \citep{neff95,oneal96,oneal98,oneal04}, or the OH 1.563 $\mu$m feature \citep{oneal01}.

@@

In this work we constrain the starspot properties of \name with 4 complementary techniques.  Section \ref{sec:obs} quantifies the optical variability of \name over the last 31 years based on all available photometric monitoring; a collection of spectral observations at various phases of variability is introduced.  Section \ref{sec:methods} and Appendix \ref{methods-details} describe a spectral inference technique aimed at generalizing line depth ratio analysis, which is applied to a high resolution panchromatic near-IR spectrum of \name in Section \ref{sec:two_tempIGRINS} .  Sections 4.1, 4.2, and 4.3 show results from SED fitting, polychromatic photometric monitoring, and optical TiO line-depth ratio fitting.  All lines of evidence are ultimately combined to build a consistent picture of the spectral and temporal evolution of \name, and what can be understood about pre-MS stellar evolution from this exemplar.

@@

An archive of 1173 $B$, $V$ and/or $R$ photometric monitoring visits was assembled from published and unpublished data sources spanning 31 years in 22 observing seasons.  Published data targeting \name\ is composed of 29 $BVR$ visits from 1985$-$1986 \citep{vrba93}, 26 $BVR$ epochs from 1990$-$1991 \citep{bouvier93}, 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 $BVR$ visits from 2013 \citep{donati14}.  ASAS3 \citep{pojmanski04} acquired 63 $V-$band measurements from 2002$-$2004.  Integral-OMC obtained 138 $V-$band measurements from 2006$-$2008 \citep{garzon12}.  The AAVSO archive \citep{kafka16} includes 385 $V$, 23 $B$ and 10 $R$ measurements from 2013$-$2016.  Finally, unpublished data from the ASAS-SN survey \citep{shappee14}, were obtained from 2012 January -- 2016 March in 186 visits.  Figure \ref{fig:PhotTime} displays all the $V-$band photometry over the interval 1986-2016.

@@

\subsection{The Spectral Energy Distribution}

@@

\subsection{Rotational modulation of the hot spot}

@@

\subsection{Rotational Modulation of TiO Depth}

@@

{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS},

>>>>

\providecommand{\eprint}[1]{\href{http://arxiv.org/abs/#1}{#1}}
\providecommand{\adsurl}[1]{\href{#1}{ADS}}
\newcommand{\name}{LkCa4 }
\newcommand{\project}[1]{\textsl{#1}}
%\def\vsini{$v\sin{i_*}$}

@@

Spectroscopic strategies have the power to measure both the starspot areal coverage and temperature in any geometric configuration.  At low resolution, SED modeling \citep{wolk96} has detected evidence for sunspots in weak-lined T-Tauri stars (WTTS).  At high resolution, line depth ratio analysis has been demonstrated mostly on evolved stars in relatively small bandwidths, namely the TiO bands \citep{neff95,oneal96,oneal98,oneal04}, or the OH 1.563 $\mu$m feature \citep{oneal01}.

@@

In this work we constrain the starspot properties of \name with 4 complementary techniques.  Section \ref{sec:obs} quantifies the optical variability of \name over the last 31 years based on all available photometric monitoring; a collection of spectral observations at various phases of variability is introduced.  Section \ref{sec:methods} and Appendix \ref{methods-details} describe a spectral inference technique aimed at generalizing line depth ratio analysis, which is applied to a high resolution panchromatic near-IR spectrum of \name in Section \ref{sec:two_tempIGRINS} .  Sections \ref{sec:SED}, \ref{sec:rotSpot}, and \ref{sec:RotTiO} show results from SED fitting, polychromatic photometric monitoring, and optical TiO line-depth ratio fitting.  All lines of evidence are ultimately combined to build a consistent picture of the spectral and temporal evolution of \name, and what can be understood about pre-MS stellar evolution from this exemplar.

@@

An archive of 1173 $B$, $V$ and/or $R$ photometric monitoring visits was assembled from published and unpublished data sources spanning 31 years in 22 observing seasons.  Published data targeting \name\ is composed of 29 $BVR$ visits from 1985$-$1986 \citep{vrba93}, 26 $BVR$ epochs from 1990$-$1991 \citep{bouvier93}, 284 visits in $V$-band (278 with $B$ and 268 with $R$) from 1992 August - 2004 October \citep{grankin08}, and 10 $BVR$ visits from 2013 \citep{donati14}.  ASAS3 \citep{pojmanski04} acquired 63 $V-$band measurements from 2002$-$2004.  Integral-OMC obtained 138 $V-$band measurements from 2006$-$2008 \citep{garzon12}.  The AAVSO archive \citep{kafka16} includes 385 $V$, 23 $B$ and 10 $R$ measurements from 2013$-$2016.  Finally, unpublished data from the ASAS-SN survey \citep{shappee14}, were obtained from 2012 January -- 2016 March in 186 visits.  Figure \ref{fig:PhotTime} displays all the $V-$band photometry over the interval 1985-2016.

@@

\subsection{The Spectral Energy Distribution}\label{sec:SED}

@@

\subsection{Rotational modulation of the hot spot}\label{sec:rotSpot}

@@

\subsection{Rotational Modulation of TiO Depth}\label{sec:RotTiO}

@@

{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, 
{\it Software: } TBD
	\project{pandas} \citep{mckinney10}
    \project{emcee} \citep{foreman13},
	\project{matplotlib} \citep{hunter07},
	\project{numpy} \citep{vanderwalt11},
	\project{scipy} \citep{jones01},
	\project{ipython} \citep{perez07},
	\project{gatspy} \citep{JakeVanderplas2015},
	\project{starfish} \citep{czekala15}
%\software{%
%	\project{pandas} \citep{mckinney10}
%    \project{emcee} \citep{foreman13},
%	\project{matplotlib} \citep{hunter07},
%	\project{numpy} \citep{vanderwalt11},
%	\project{scipy} \citep{jones01},
%	\project{ipython} \citep{perez07},
%	\project{gatspy} \citep{JakeVanderplas2015},
%	\project{starfish} \citep{czekala15}}.
